---
title: "week_5_lab_2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### A. Improve this regular R code by abstracting the main activities in your own new function.

```{r}
#  Can you improve this analysis code?
df <- data.frame(a=1:10, b=seq(200,400,length=10),c=11:20,d=NA) 
df$a <- (df$a - min(df$a)) / (max(df$a) - min(df$a))
df$b <- (df$b - min(df$a)) / (max(df$b) - min(df$b))
df$c <- (df$c - min(df$c)) / (max(df$c) - min(df$c))
df$d <- (df$d - min(df$d)) / (max(df$a) - min(df$d)) 
```

```{r eval=FALSE}
## Simplify to work with a generic vector named “x” 
## Note that we call the min() function twice…
xmin <- min(x)
x <- (x - xmin) / (max(x) - xmin)
```

```{r eval=FALSE}
## Further optimization to use the range() function… 
rng <- range(x)
x <- (x - rng[1]) / (rng[2] - rng[1])
```

```{r}
# You need a “name”, “arguments” and “body”… 
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
# Test on a small example where you know the answer
rescale(1:10)
```

```{r}
df
```

```{r}
rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) { 
 plot(answer, typ="b", lwd=4) 
 }
 print("I can see it in ...")
}
```

```{r}
rescale(df$a, plot = TRUE)
```

```{r}
rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=TRUE)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) { 
 plot(answer, typ="b", lwd=4) 
 }
print("I can see it in ...")
return(answer)
}
```


```{r}
rescale(df$a, plot=T)
```

### B. Next improve the below example code for the analysis of protein drug interactions by abstracting the main activities in your own new function.

```{r}
# Can you improve this analysis code?

library(bio3d)
s1 <- read.pdb("C:/Users/User/Bioinformatics/BGGN-213/Week_5/R_week5/class06/4ake.pdb") # kinase with drug
s3 <- read.pdb("C:/Users/User/Bioinformatics/BGGN-213/Week_5/R_week5/class06/1e4y.pdb") # kinase with drug
s2 <- read.pdb("C:/Users/User/Bioinformatics/BGGN-213/Week_5/R_week5/class06/1ake.pdb") # kinase no drug
# s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
# s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
# s3.chainA <- trim.pdb(s3, chain="A", elety="CA")
# s1.b <- s1.chainA$atom$b
# s2.b <- s2.chainA$atom$b
# s3.b <- s3.chainA$atom$b
# plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor") 
# plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor") 
# plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")

```

```{r}
#' Title
#'
#' @param x 
#'
#' @return
#' @export
#'
#' @examples
plot_pdb <- function(x){
  x.chainA <- trim.pdb(x, chain="A", elety="CA")
  x.b <- x.chainA$atom$b
  plotb3(x.b,sse = x.chainA, type = "l", ylab = "Bfactor")}
```

```{r}
plot_pdb(s1)
```


```{r}
plot_pdb(s2)
```

```{r}
plot_pdb(s3)
```


<span style = "color:red;"><b>Q1.</b> What type of object is returned from the read.pdb() function?</span>
<!-- Q1.What type of object is returned from the read.pdb() -->

<font color = "red"><b>Q2.</b> What does the <b>trim.pdb()</b> function do?</font>

<font color = "red"><b>Q3.</b> What input parameter would turn off the marginal black and grey rectangles in the plots and what do they represent in this case? </font>

<font color = "red"><b>Q4.</b> What would be a better plot to compare across the different proteins?  </font>

<font color="red"> <b>Q5.</b> Which proteins are more similar to each other in their B-factor trends. How could you quantify this?</font> <font color = "green"> HINT: try the rbind(), dist() and hclust() functions together with a resulting dendrogram plot. Look up the documentation to see what each of these functions does.</font>

