---
title: "Week_5_R_function_lab_1"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



**Q1**. Write a function **grade()** to determine an overall grade from a vector of student homework
assignment scores dropping the lowest single score. If a student misses a homework (i.e. has an
**NA** value) this can be used as a score to be potentially dropped. Your final function should be
adquately explained with code comments and be able to work on an example class gradebook
such as this one in CSV format: “https://tinyurl.com/gradeinput” [**3pts**]


### Example input vectors to start with
```{r}
# Example input vectors to start with
student1 <- c(100, 100, 100, 100, 100, 100, 100, 90)
student2 <- c(100, NA, 90, 90, 90, 90, 97, 80)
student3 <- c(90, NA, NA, NA, NA, NA, NA, NA)
```

```{r}
student1
mean(student1)
min(student1)
```

To find the position of the smallest value use the `which.min()`

```{r}
which.min(student1)
student1[which.min(student1)]
```

to get everything except the min value 
```{r}
student1[-which.min(student1)]
mean(student1[-which.min(student1)])
```

```{r}
student2
mean(student2, na.rm = TRUE)
mean(student2[-2])
```

```{r}
student3
mean(student3,na.rm = T)
mean(student3)
```

Change the NA values to zero
use `is.na()` function to identify NA value in the vector
```{r}
is.na(student2)
student2[is.na(student2)]

x<- student3
student3[is.na(student3)]<-0
x
mean(x)
mean(x[-which.min(x)])
x[which.min(x)]
which.min(x)

```


### Making the function

```{r}
#' Title
#'
#' @param x 
#'
#' @return
#' @export
#'
#' @examples
grade <- function(x){
# map NA missing homework values to zero 
# missing homework scores zero
  x[is.na(x)] <-0
#  print(x)
# print(mean(x)) 
  # excluding the lowest value score homework
  print(mean(x[-which.min(x)]))
}

```

```{r}

grade(student3)
grade(student2)
grade(student1)
```


```{r}
gradebook = read.csv(file ="C:/Users/User/Bioinformatics/BGGN-213/Week_5/R_week5/class06/student_homework (1).csv", row.names = 1)
# data
# row.names(data)
```

```{r}
apply(gradebook,1,grade)
```

```{r}
results<-apply(gradebook, 1, grade)
sort(results)
```
```{r}
which.max(results) 
```

```{r}
hw.ave<-apply(gradebook,2,mean, na.rm=TRUE)
which.min(hw.ave)
hw.ave
```
```{r}
hw.med <- apply(gradebook, 2, median, na.rm=T)
which.min(hw.med)
hw.med
```
Plot the data using `boxplot()`

```{r}
boxplot(gradebook)
```
```{r}
results
cor(results,gradebook)
```

```{r}
gradebook[is.na(gradebook)]<-0
gradebook
apply(gradebook,2,cor, x=results)
```



**Q2.** Using your **grade()** function and the supplied [gradebook](https://tinyurl.com/gradeinput), Who is the top scoring student
overall in the gradebook? [**3pts**]

**Q3.** From your analysis of the gradebook, which homework was toughest on students (i.e. obtained
the lowest scores overall? [**2pts**]

**Q4.** *Optional Extension:* From your analysis of the gradebook, which homework was most
predictive of overall score (i.e. highest correlation with average grade score)? [**1pt**]

**Q5.** Make sure you save your Rmarkdown document and can click the **“Knit”** button to generate
a PDF foramt report without errors. Finally, submit your PDF to gradescope. [**1pt**]


